Research Cases

### 2025-10-09 Code/R/Research/cases_research.Rmd
code for precision research in different cases

```{r}
# no rates
rates.true <- c(0, 0)
plot.name <- "_no_rates"
# both rates -0.01
# rates.true <- c(-0.01, -0.01)
# plot.name <- "_small_eq_rates"
# both rates -0.02
# rates.true <- c(-0.02, -0.02)
# plot.name <- "_large_eq_rates"
# rates from paper
# rates.true <- c(-0.01, -0.02)
# plot.name <- ""

freqs.true <- c(0.2, 0.22)
N <- 25

@@

```{r}
R <- 40

ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_ssa_rec, rmse_ts_nd, signal, seed = 5)
hossa_err <- calc_errors_by_params(params_grid_hossa, R, pred_hossa_rec, rmse_ts_nd, signal, seed = 5)
```

>>>>

```{r}
# no rates
rates.true <- c(0, 0)
rates_case <- "_no_rates"
# both rates -0.01
# rates.true <- c(-0.01, -0.01)
# plot.name <- "_small_eq_rates"
# both rates -0.02
# rates.true <- c(-0.02, -0.02)
# plot.name <- "_large_eq_rates"
# rates from paper
# rates.true <- c(-0.01, -0.02)
# plot.name <- "_regular_rates"

# no freqs
# freqs.true <- c(0, 0)
# freqs_case <- "_no_freqs"
# different freqs
freqs.true <- c(0.2, 0.22)
freqs_case <- "_regular_freqs"
# close freqs
# freqs.true <- c(0.02, 0.0205)
# freqs_case <- "_close_freqs"

N <- 25

@@

```{r}
R <- 500

ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_ssa_rec, rmse_ts_nd, signal, seed = 5)
hossa_err <- calc_errors_by_params(params_grid_hossa, R, pred_hossa_rec, rmse_ts_nd, signal, seed = 5)
save(ssa_err, hossa_err, file = paste0("./comp_results/cases_errors/sum_of_2_complex_periodics", rates_case, freqs_case, ".RData"))
```
